%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
\vspace{-1mm}

%---------------------------------------------------------
\cventry\textbf{}
    {Software Development Engineer 2} % Job title
    {Adobe Systems} % Organization
    {Noida} % Location
    {August 2020 - Present} % Date(s)
    {
        \vspace{-4mm}
        \item \textbf{Responsibility:} 
        \begin{itemize}
            \item Independently managed entire \textbf{build} and \textbf{assembly} \textbf{pipelines} for various products including \textbf{Creative Cloud Desktop} Family of products consisting of \textbf{50+ repositories}. Pipelines included \textbf{nightly}, \textbf{incremental}, \textbf{on-demand} as well as \textbf{Pull request} builds. Ensuring these pipelines are up-to-date with industry standards and available at all times with the best possible performance on the provided resources. Managed various releases, hot fixes, and patches for assigned products with regular monitoring. Creating installers for different Operating Systems, Mobile Apps and \textbf{Docker/Kubernetes}-based services for both \textbf{metal} and \textbf{cloud}.
            \item Automated and refactored 50+ components for Creative Cloud Desktop and partner teams.
            \item Mentored multiple Junior Members of the team.
        \end{itemize}
        \item \textbf{Achievements:}
        \begin{itemize}
            \item Received \textbf{2 Spot awards} for excellent performance, innovation and team cooperation.
            \item Reduced deliverable time by \textbf{70\%} on average. Distributed build and efficient pipeline.
            \item Automated more than \textbf{80\%} of manual work. Removed error-prone processes and manual intervention.
            \item Improved build system reliability. Continuous monitoring and fixes.
            \item Solely created \textbf{Flyover} which is now the preferred library for writing Jenkins pipeline by multiple teams w/o any automation background.
        \end{itemize}
        \item \textbf{Flyover (Owner):}
        \begin{itemize}
            \item Made pipeline development as easy as writing \textbf{JSON} by designing and developing a \textbf{dynamic}, \textbf{JSON}-like configuration-driven pipeline writing library with \textbf{Groovy/Java} for \textbf{Jenkins}.
            \item Revamped scripted pipelines with \textbf{Object-Oriented principles} providing smaller, reusable, testable components and integration harness.
        \end{itemize}
        \item \textbf{Release Engineering Support System:} 
        \begin{itemize}
            \item Designed and developed a generic config driver build system written in \textbf{JavaScript} and \textbf{NodeJs} for CI/CD pipelines and migrated all the responsible repos to RESS. 
            \item Packaged these as \textbf{Grunt plugins} and distributed them as \textbf{npm} packages via private \textbf{Artifactory}.
        \end{itemize}
        \item \textbf{PodCast (Owner):} 
        \begin{itemize}
            \item Dynamic agent for \textbf{Jenkins}. \textbf{Cloud-ready} solution for modern build pipeline using \textbf{Kubernetes}. 
            \item Providing \textbf{horizontal scaling} of agents, containerized builds, bundled environment and guaranteed reproducibility of builds. More efficient packing of pipeline resulting in more throughput.
        \end{itemize}
        \item \textbf{Virtualization (Owner):}
        \begin{itemize}
            \item Implemented \textbf{Openstack} Virtual machines for quick creation and infrastructure setup with volume and snapshots.
            \item POC on \textbf{macOS} virtual machines using QEMU and native virtualization framework solution for Apple silicon. Explored \textbf{OCI} image-based solution for storage and distribution of macOS virtual machines.
        \end{itemize}
        \item \textbf{Ansible:} \textbf{Infrastructure as Code} (IaC) and \textbf{Configuration as Code} (CaC). Automating infrastructure setup for Linux, macOS and Windows hosts.
    }

\vspace{-1mm}

%---------------------------------------------------------
\cventry
    {Intern} % Job title
    {Hexagon Capability Center India} % Organization
    {Hyderabad} % Location
    {May 2019 - July 2019} % Date(s)
    {
        Taxi trajectory analysis using \textbf{PyTorch} and \textbf{GPU} inference in private data centres. Leveraged \textbf{deep learning} techniques to extract valuable insights from extensive datasets, optimizing route planning and accurately predicting demand for enhanced transportation systems and efficient taxi operations.
    }

\end{cventries}

\vspace{-2mm}
